Computational methods in landscape ecology

### 2024-09-20 Manuscript.qmd
Update layout

author:
  - name: Maximilian H.K. Hesselbarth
    orcid: 0000-0003-1125-9918
    email: mhk.hesselbarth@gmail.com
    affil-id: 1
  - name: Jakub Nowosad
    orcid: 0000-0002-1057-3721
    email: nowosad.jakub@gmail.com
    affil-id: 2,3
  - name: Craig E. Simpkins
    orcid: 0000-0003-3212-1379
    email: simpkinscraig063@gmail.com
    affil-id: 4
  - name: Martin Jung
    orcid: 0000-0002-7569-1390
    email: jung@iiasa.ac.at
    affil-id: 1
  - name: Alida de Flamingh
    orcid: 0000-0003-1223-6654
    email: adeflamingh@gmail.com
    affil-id: 5
  - name: Gemma Gerber
    orcid: 0000-0002-8722-3113
    email: gerber@iiasa.ac.at
    affil-id: 1
  - name: Martí Bosch
    orcid: 0000-0001-8735-9144
    email: marti.bosch@epfl.ch
    affil-id: 6

affiliations:
  - id: 1
    name: International Institute for Applied Systems Analysis, Biodiversity, Ecology, and Conservation Group, Laxenburg, Austria
  - id: 2
    name: Adam Mickiewicz University, Poznań, Poland
  - id: 3
    name: University of Münster, Münster, Germany
  - id: 4
    name: Auckland Council, Environmental Services, Auckland, New Zealand
  - id: 5
    name: Carl R. Woese Institute for Genomic Biology, University of Illinois at Urbana-Champaign, Urbana, IL, USA
  - id: 6
    name: École polytechnique fédérale de Lausanne, Lausanne, Switzerland

format:
  pdf:
    keep-tex: true
    template-partials:
      - title.tex
    include-in-header:
      text: |
        \usepackage{lineno}\linenumbers
        \usepackage[noblocks]{authblk}
        \usepackage{setspace}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
papersize: a4paper
fontsize: 10pt
geometry: margin=25mm
indent: 2m
linestretch: 1.5
number-sections: false

@@

\noindent Keywords: (1) spatial data, (2) spatial patterns, (3) pattern-process link (4) open-source, (5) scientific software

>>>>

author:
  - name: Maximilian H.K. Hesselbarth
    affil-id: 1
  - name: Jakub Nowosad
    affil-id: 2,3
  - name: Alida de Flamingh
    affil-id: 4
  - name: Craig E. Simpkins
    affil-id: 5
  - name: Martin Jung
    affil-id: 1
  - name: Gemma Gerber
    affil-id: 1
  - name: Martí Bosch
    affil-id: 6

affiliations:
  - id: 1
    name: International Institute for Applied Systems Analysis, Biodiversity, Ecology, and Conservation Group, Laxenburg, Austria
  - id: 2
    name: Adam Mickiewicz University, Poznań, Poland
  - id: 3
    name: University of Münster, Münster, Germany
  - id: 4
    name: Carl R. Woese Institute for Genomic Biology, University of Illinois at Urbana-Champaign, Urbana, IL, USA 
  - id: 5
    name: Auckland Council, Environmental Services, Auckland, New Zealand
  - id: 6
    name: École polytechnique fédérale de Lausanne, Lausanne, Switzerland

format:
  pdf:
    keep-tex: true
    template-partials:
      - title.tex
    include-in-header:
      text: |
        \usepackage{academicons}
        \usepackage{fontawesome5}
        \usepackage{lineno}\linenumbers
        \usepackage[noblocks]{authblk}
        \usepackage{setspace}
        \renewcommand\Affilfont{\footnotesize}
        \newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\aiOrcid#1}}}
        \newcommand{\mail}[1]{\href{mailto:#1}{\textcolor[HTML]{052E81}{\faEnvelope#1}}}

papersize: a4paper
mainfont: Garamond
fontsize: 11pt
geometry: margin=25mm
indent: 2m
linestretch: 1.5
number-sections: false

@@

\noindent \footnotesize M.H.K. Hesselbarth \orcid{0000-0003-1125-9918} \mail{mhk.hesselbarth@gmail.com}

\noindent \footnotesize J. Nowosad \orcid{0000-0002-1057-3721}

\noindent \footnotesize A. de Flamingh \orcid{0000-0003-1223-6654}

\noindent \footnotesize C.E. Simpkins \orcid{0000-0003-3212-1379}

\noindent \footnotesize M. Jung \orcid{0000-0002-7569-1390}

\noindent \footnotesize G. Gerber \orcid{0000-0002-8722-3113}

\noindent \footnotesize M. Bosch \orcid{0000-0001-8735-9144}

\noindent \small \textit{Keywords: (1) spatial data, (2) spatial patterns, (3) pattern-process link (4) open-source, (5) scientific software}
